\chapter{Conclusion}\label{ch:floquet-discussion}

In Part 2 of this thesis, we have demonstrated time-crystalline behavior shares a close relationship not only to disordered interactions but also to disorder in the driving part. The unifying concept key to understanding the described phenomena is the role of long-range order of the eigenstates (described well in e.g~\cite{vonkeyserlingkAbsoluteStabilitySpatiotemporal2016,elsePrethermalPhasesMatter2017}). In \autoref{ch:metronome-spin}, the high sensitivity of the lifetime of the whole system to the variation of the driving field on just a single site is testament to the underlying long-range order - in that case of the ground state of an Ising model. States at higher temperature do not possess long range order and thus do show neither time crystalline behavior nor lifetime enhancements. Viewing the driven pair model of \autoref{ch:rydberg-timecrystal} through this lens, it becomes apparent that no true time crystal can be expected at this level: The lowest order of the pair model just does not feature any interaction terms among the pairs and so no long-range order can be generated. Whether pair-pair interactions can change this fundamentally is questionable because there is a crucial difference to the Ising model: All eigenstates of an Ising interaction, i.e. $\sum_{ij} J_{ij}S_{z}^{(i)}S_{z}^{(j)}$, written in the symmetric sector of its $\mathbb{Z}_2$ symmetry feature long-range order because they are superpositions of the form $\ket{\psi}\pm X\ket{\psi}$, where $X$ is the generator of the symmetry. In contrast, this is not true for eigenstates of the pair model because each $H_{pair}$ has $\ket{\pm}\propto\ket{\uparrow\downarrow}\pm \ket{\downarrow\uparrow}$ as possible eigenstates which are symmetric under spin-flip. Thus the eigenstates for the pair model can fulfill the symmetry in local patches destroying the global long-range order in the process.

A consequence of this interpretation is that one learns about the structure of the eigenstates from the measurement of the time crystal protocol. An interesting application of this could be to study whether we can restore the time crystal signature by using different parameter regimes. The flexibility of the Rydberg platform allow for tuning the strength of not only Ising interactions but also of random on-site potentials which are generated through van der Waals interactions of neighboring spins~\cite{wuProgrammableOrderDisorder2024}. So one could use the existence of a time crystal as an indicator to probe the crossover between XXZ and Ising models and thus the transition between pair localization and traditional Ising-like MBL. While MBL is conjectured to be absent for long-range interaction $\alpha < 2d$ by resonance counting arguments~\cite{yaoManyBodyLocalizationDipolar2014,burinLocalizationRandomXY2015}, these estimates used coefficients of the same magnitude for Ising and hopping terms and so the Ising limit of power-law XXZ models is not studied to our knowledge.
%long-range order
%
%This insight could be useful in understanding whether the experimental system of Part 1 could potentially show stable time-crystalline signatures. Preliminary experimental results indicate that interactions indeed appear to stabilize the magnetization dynamics of a spatially disordered XX model under repeated imperfect flips about its $x$-axis (cf. Fig.~\ref{fig:rydberg-timecrystal-experiment}). However, a naive calculation in the pair model does not find any true stabilization and instead predicts a decay of the magnetization's envelope on a timescale $\propto\epsilon^2$~\footnote{Note that the graphic uses a different definition for the rotation angle. It uses $\phi=\epsilon \pi$ and thus $\epsilon = 1$ is the soluble point. In contrast this thesis uses $\phi=(1-\epsilon)\pi$ with $\epsilon=0$ being soluble.}. The reason the continuous slow decay are in the end the pairs themselves: Since the system essentially decomposes into non-interacting two-spin subsystems each decaying on a timescale $\propto \epsilon^2/J$, taking the thermodynamic limit cannot cause stabilization. In part this is also due to phase-wrapping effects, which limits a pair's interaction strength $J$ effective to the interval $[0,\pi]$. Since it is so far unclear whether this system is truly a time-crystal or not, we can explore other mechanism in search for potential stabilization. 
%
%One unexplored route is the influence of van der Waals interactions which effectively cause locally varying $z$-fields. One way to interpret these is that they change the alignment of the driving field spatially. As we have seen in this part of the thesis, such a spatially varying driving field can help stabilizing time crystalline dynamics.
%
%Another exciting avenue to follow is to consider the interactions among pairs. As we derived in Chapter~\ref{sec:universal-dynamics}, for an XXZ model, these pair-pair interactions take the form of an effective Ising model. Since Ising models as the prototypical example for time crystals, we deem this a very promising approach in the case of XXZ models. However, in XX models this effective Ising term does not exists to first order. So in order to access stabilization effects due to pair-pair interactions a better understanding of the higher orders of the perturbation theory is required.
%
%
%
